Groth16 zk-SNARK Proof Verification on Freeton : Three Use Cases

### 2021-07-14 submission/submission.tex
Update of section 4 pincode

In this use case, we use \zksnarks{} to allow users to replace their
public keys in multisig wallets. The typical use is when a user has
lost the associated secret key, and is unable to sign/confirm any new
transaction. With our approach, the user first creates a recovery
contract, where a passphrase is associated to his public key. If he
needs to change his public key, he can use \zksnarks{} to associate a new
public key in his recovery contract, and tell multisig wallets to
safely replace his pubkey by the new one.

Compared to other approaches, this use can provide several
improvements:
\begin{itemize}
\item The user does not disclose his passphrase. Most other approaches
  (based on hashes for example) give an opportunity for
  man-in-the-middle attacks ;
\item As the user does not disclose his passphrase, the pubkey can be
  replaced several times ;
\item The user does not need to create the new public key ahead of
  time. Instead, he can create it when he has lost the former one,
  decreasing the likelihood of losing the associated secret key also ;
\end{itemize}

@@

This use case includes 3 different components:
\begin{description}
\item[PinCode Client:] it is a C++ program linked to the Blueprint
  \zksnarks{} library. It can be used in two different ways:
  \begin{itemize}
  \item To create the initial circuit using the passphrase. The client
    should be called as:
\begin{verbatim}
pincode-client prepare "my pass phrase"
\end{verbatim}
   This will generate a file \lstinline{verifkey.hex} that can be used
   as an argument when deploying the \lstinline{PubkeyRecovery} smart
   contract, and a file \lstinline{provkey.hex} that can be used to
   create new witnesses ;
 \item To create a witness that the passphrase is known when providing
   a new public key. Because the witness contains the new public key,
   an attacker cannot intercept the message and replace it. The client
   should be called as:
\begin{verbatim}
pincode-client prove "my pass phrase" "PUBKEY_AS_HEX_NUMBER"
\end{verbatim}
  The command expects to find the file \lstinline{provkey.hex} and
  generates a file \lstinline{proof.hex} that should be submitted to
  the \lstinline{PubkeyRecovery} smart contract together with the new
  public key.
  \end{itemize}
\item[PubkeyRecovery smart contract:] This smart contract is a TIP-3
  contract, using the initial public key to verify its address. This
  contract is very simple. It contains:
  \begin{itemize}
  \item A constructor to set the circuit that will be used to verify
    that the passphrase is known when it is used ;
  \item An external function
    \lstinline{SetNewPubkey(bytes proof, uint256 pubkey)}
    to define the new public key, while providing a
    proof of knowledge of the passphrase ;
  \item An external function
    \lstinline{RecoverPubkey(address multisigaddr)}
    to call a multisig contract to update the
    corresponding custodian. The multisig contract will verify that
    the address is correct before replacing the public key ;
  \end{itemize}
\item[Modified Multisig Wallet:] This is a standard multisig wallet,
  modified to recognize addresses of \lstinline{PubkeyRecovery} smart
  contracts. They provide two additionnal functions:
  \begin{itemize}
  \item An external function
    \lstinline{SetPubkeyRecoveryCode(TvmCell code)}
    to define the code of the \lstinline{PubkeyRecovery} smart
    contract. Because the code hash is known, anybody can call this
    function with the correct code.
  \item An external function
    \lstinline{RecoverPubkey(uint256 oldkey, uint256 newkey)}
    that can only be called by a
    \lstinline{PubkeyRecovery} smart contract.
  \end{itemize}
\end{description}

@@

In particular:
\begin{itemize}
\item The interface has been improved to provide multiple levels of
  subcommands, making them easier to understand and to use ;
\item A new argument {\tt --image} is available with {\tt ft switch
  create} to specify the Docker image to use. This new argument is
  specially useful for our Docker image for NilFoundation TONOS SE.
\end{itemize}

>>>>

In this use case, we use \zksnarks{} to allow users to replace their
public keys in other contracts, for example multisig wallets. The
typical use is when a user has lost the associated secret key, and is
unable to sign/confirm any new transaction. With our approach, the
user first creates a recovery contract, where a passphrase is
associated to his public key. If he needs to change his public key, he
can use \zksnarks{} to associate a new public key in his recovery
contract, and tell other contracts to safely replace his pubkey by the
new one.

Compared to other approaches, this use can provide several
improvements:
\begin{itemize}
\item The user does not disclose his passphrase. Most other approaches
  (based on hashes for example) give an opportunity for
  man-in-the-middle attacks;
\item As the user does not disclose his passphrase, the pubkey can be
  replaced several times;
\item The user does not need to create the new public key ahead of
  time. Instead, he can create it when he has lost the former one,
  decreasing the likelihood of losing the associated secret key also;
\end{itemize}

@@

This use case includes 3 different components:
\begin{description}
\item[PinCode Client:] it is a C++ program linked to the Blueprint
  \zksnarks{} library. It can be used in two different ways:
  \begin{itemize}
  \item To create the initial circuit using the passphrase. The client
    should be called as:
\begin{verbatim}
pincode-client prepare "my pass phrase"
\end{verbatim}
   This will generate a file \lstinline{verifkey.hex} that can be used
   as an argument when deploying the \lstinline{PubkeyRecovery} smart
   contract, and a file \lstinline{provkey.hex} that can be used to
   create new witnesses;
 \item To create a witness that the passphrase is known when providing
   a new public key. Because the witness contains the new public key,
   an attacker cannot intercept the message and replace it. The client
   should be called as:
\begin{verbatim}
pincode-client prove "my pass phrase" "PUBKEY_AS_HEX_NUMBER"
\end{verbatim}
  The command expects to find the file \lstinline{provkey.hex} and
  generates a file \lstinline{proof.hex} that should be submitted to
  the \lstinline{PubkeyRecovery} smart contract together with the new
  public key.
  \end{itemize}
\item[PubkeyRecovery smart contract:] This smart contract is a
  contract à la TIP-3 contract, using the initial public key to verify
  its address. This contract is very simple. It contains:
  \begin{itemize}
  \item A constructor to set the circuit that will be used to verify
    that the passphrase is known when it is used;
  \item An external function
    \lstinline{SetFromPincode(bytes proof, uint256 pubkey)}
    to define the new public key, while providing a
    proof of knowledge of the passphrase;
  \item An external function
    \lstinline{RecoverPubkey(RecoverablePubkey addr)} to call a
    recoverable contract to update the corresponding pubkey.
  \end{itemize}
\item[Abstract RecoverablePubkey contract:] This is an abstract
  contract, from which other contracts should inherit to be able to
  benefit from the {\tt PubkeyRecovery} mechanism. The contract
  provides two main functions:
  \begin{itemize}
  \item An external function \lstinline{SetPubkeyRecoveryCode(TvmCell
    code)} to define the code of the \lstinline{PubkeyRecovery} smart
    contract. Because the code hash is known (inlined in the code),
    anybody can call this function with the correct code.
  \item An external function \lstinline{RecoverPubkey(uint256 oldkey,
    uint256 newkey)} that can only be called by a
    \lstinline{PubkeyRecovery} smart contract. The function verifies
    that the address belongs to such a contract before calling a
    function \lstinline{recover\_pubkey(oldkey, newkey)}, that the
    inheriting contract should define to specify the business logic
    that should happen when a pubkey is replaced.
  \end{itemize}
\item[Modified Multisig Wallet:] The
  \lstinline{RecoverableMultisigWallet} contract is the standard
  multisig wallet of Surf, updated for version 0.40 of Solidity, and
  modified to inherit from the \lstinline{RecoverablePubkey}
  contract. It defines the business logic to replace a custodian key.
  For that, it first checks that the old key belongs to an existing
  custodian of the contract, that the new key does not belong to an
  existing custodian, and then replace the old key by the new one,
  associated to the same index (for bitfields).
\end{description}

@@

In particular:
\begin{itemize}
\item The interface has been improved to provide multiple levels of
  subcommands, making them easier to understand and to use;
\item A new argument {\tt --image} is available with {\tt ft switch
  create} to specify the Docker image to use. This new argument is
  specially useful for our Docker image for NilFoundation TONOS SE.
\end{itemize}
